---
title: "Exploratory Sustainability Survey Analysis"
author: "Blain Morin"
date: "January 21, 2020"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE)

library(dplyr)
library(ggplot2)
library(stringr)
library(gridExtra)
library(ggridges)
library(readr)
library(scales)
library(ggcorrplot)


survey = read_csv("2019 Campus Sustainability Survey - Final_January 9, 2020_13.47.clean.deidentified.Jeff.csv")

```

```{r}

### Select my columns
mydata = survey[, c(11:25, 41:49, 56:68, 191:194, 223:301, 304:305, 314, 316, 326:328)]
mydata = mydata[-c(1,2), ]

```

# Jeff's Questions

## To What Extent does "sustainability" involve the following dimensions?

### Environmental Outcomes

```{r}

### Environmental Outcomes

mydata = mydata %>%
  filter(Q102_1 != "-99") %>%
  mutate(Q102_1 = ifelse(Q102_1 == "Never", "1", Q102_1)) %>%
  mutate(Q102_1 = ifelse(Q102_1 == "Rarely", "2", Q102_1)) %>%
  mutate(Q102_1 = ifelse(Q102_1 == "Sometimes", "3", Q102_1)) %>%
  mutate(Q102_1 = ifelse(Q102_1 == "Frequently", "4", Q102_1)) %>%
  mutate(Q102_1 = ifelse(Q102_1 == "Very Frequently", "5", Q102_1)) %>%
  mutate(Q102_1 = as.numeric(Q102_1)) 
  
  
mydata %>%
  filter(Pol.aff != "-99") %>%
  filter(Pol.aff != "Other (please describe):")%>%
  filter(Pol.aff != "Libertarian") %>%
  ggplot(aes(x = Q102_1)) +
  geom_density_ridges(aes(y = Pol.aff, fill = Pol.aff)) +
  facet_wrap(~Gender) +
  ylab("") +
  xlab("1 = Never, 5 = Very Frequently") +
  ggtitle("Density Plot: Environmental Outcomes, By Gender") +
  theme_classic() +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("#619CFF", "#00BA38", "#F8766D"))


```

### Economic Outcomes

```{r}

### Economic Outcomes

mydata = mydata %>%
  filter(Q102_2 != "-99") %>%
  mutate(Q102_2 = ifelse(Q102_2 == "Never", "1", Q102_2)) %>%
  mutate(Q102_2 = ifelse(Q102_2 == "Rarely", "2", Q102_2)) %>%
  mutate(Q102_2 = ifelse(Q102_2 == "Sometimes", "3", Q102_2)) %>%
  mutate(Q102_2 = ifelse(Q102_2 == "Frequently", "4", Q102_2)) %>%
  mutate(Q102_2 = ifelse(Q102_2 == "Very Frequently", "5", Q102_2)) %>%
  mutate(Q102_2 = as.numeric(Q102_2)) 


mydata %>%
  filter(Pol.aff != "-99") %>%
  filter(Pol.aff != "Other (please describe):")%>%
  filter(Pol.aff != "Libertarian") %>%
  ggplot(aes(x = Q102_2)) +
  geom_density_ridges(aes(y = Pol.aff, fill = Pol.aff)) +
  facet_wrap(~Gender) +
  ylab("") +
  xlab("1 = Never, 5 = Very Frequently") +
  ggtitle("Density Plot: Economic Outcomes, By Gender") +
  theme_classic() +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("#619CFF", "#00BA38", "#F8766D"))


```

### Social Outcomes

```{r}

### Social Outcomes

mydata = mydata %>%
  filter(Q102_3 != "-99") %>%
  mutate(Q102_3 = ifelse(Q102_3 == "Never", "1", Q102_3)) %>%
  mutate(Q102_3 = ifelse(Q102_3 == "Rarely", "2", Q102_3)) %>%
  mutate(Q102_3 = ifelse(Q102_3 == "Sometimes", "3", Q102_3)) %>%
  mutate(Q102_3 = ifelse(Q102_3 == "Frequently", "4", Q102_3)) %>%
  mutate(Q102_3 = ifelse(Q102_3 == "Very Frequently", "5", Q102_3)) %>%
  mutate(Q102_3 = as.numeric(Q102_3)) 


mydata %>%
  filter(Pol.aff != "-99") %>%
  filter(Pol.aff != "Other (please describe):")%>%
  filter(Pol.aff != "Libertarian") %>%
  ggplot(aes(x = Q102_3)) +
  geom_density_ridges(aes(y = Pol.aff, fill = Pol.aff)) +
  facet_wrap(~Gender) +
  ylab("") +
  xlab("1 = Never, 5 = Very Frequently") +
  ggtitle("Density Plot: Social Outcomes, By Gender") +
  theme_classic() +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("#619CFF", "#00BA38", "#F8766D"))


```

# deGroot Egoistic Values

```{r}

### Social Power Corrected

mydata = mydata %>%
  filter(deGroot_3 != "-99") %>%
  mutate(deGroot_3 = ifelse(deGroot_3 == "Important (3)", "3", deGroot_3)) %>%
  mutate(deGroot_3 = ifelse(deGroot_3 == "Not important (0)", "0", deGroot_3)) %>%
  mutate(deGroot_3 = ifelse(deGroot_3 == "Of supreme importance (7)", "7", deGroot_3)) %>%
  mutate(deGroot_3 = ifelse(deGroot_3 == "Opposed to my Values (-1)", "-1", deGroot_3)) %>%
  mutate(deGroot_3 = ifelse(deGroot_3 == "Very important (6)", "6", deGroot_3)) %>%
  mutate(deGroot_3 = as.numeric(deGroot_3)) %>%
  mutate(deGroot_3 = deGroot_3 + 1)

mydata %>%
  filter(Gender != "#N/A") %>%
  ggplot(aes(x = deGroot_3)) +
  geom_density(aes(color = Gender), size = 2) +
  facet_wrap(~RaceEthnicity) +
  ylab("Density") +
  xlab("0 = Opposed to my Values, 8 = Of Supreme Importance") +
  ggtitle("Social Power: Control Over Others") +
  theme_classic() 


```

```{r}

### Wealth Corrected

mydata = mydata %>%
  filter(deGroot_4 != "-99") %>%
  mutate(deGroot_4 = ifelse(deGroot_4 == "Important (3)", "3", deGroot_4)) %>%
  mutate(deGroot_4 = ifelse(deGroot_4 == "Not important (0)", "0", deGroot_4)) %>%
  mutate(deGroot_4 = ifelse(deGroot_4 == "Of supreme importance (7)", "7", deGroot_4)) %>%
  mutate(deGroot_4 = ifelse(deGroot_4 == "Opposed to my Values (-1)", "-1", deGroot_4)) %>%
  mutate(deGroot_4 = ifelse(deGroot_4 == "Very important (6)", "6", deGroot_4)) %>%
  mutate(deGroot_4 = as.numeric(deGroot_4)) %>%
  mutate(deGroot_4 = deGroot_4 + 1)

mydata %>%
  filter(Gender != "#N/A") %>%
  ggplot(aes(x = deGroot_4)) +
  geom_density(aes(color = Gender), size = 2) +
  facet_wrap(~RaceEthnicity) +
  ylab("Density") +
  xlab("0 = Opposed to my Values, 8 = Of Supreme Importance") +
  ggtitle("Wealth: Material Possessions") +
  theme_classic() 


```

```{r}

### Authority Corrected

mydata = mydata %>%
  filter(deGroot_5 != "-99") %>%
  mutate(deGroot_5 = ifelse(deGroot_5 == "Important (3)", "3", deGroot_5)) %>%
  mutate(deGroot_5 = ifelse(deGroot_5 == "Not important (0)", "0", deGroot_5)) %>%
  mutate(deGroot_5 = ifelse(deGroot_5 == "Of supreme importance (7)", "7", deGroot_5)) %>%
  mutate(deGroot_5 = ifelse(deGroot_5 == "Opposed to my Values (-1)", "-1", deGroot_5)) %>%
  mutate(deGroot_5 = ifelse(deGroot_5 == "Very important (6)", "6", deGroot_5)) %>%
  mutate(deGroot_5 = as.numeric(deGroot_5)) %>%
  mutate(deGroot_5 = deGroot_5 + 1)

mydata %>%
  filter(Gender != "#N/A") %>%
  ggplot(aes(x = deGroot_5)) +
  geom_density(aes(color = Gender), size = 2) +
  facet_wrap(~RaceEthnicity) +
  ylab("Density") +
  xlab("0 = Opposed to my Values, 8 = Of Supreme Importance") +
  ggtitle("Authority: The Right to Lead or Command") +
  theme_classic() 


```

```{r}

### Influential Corrected

mydata = mydata %>%
  filter(deGroot_1 != "-99") %>%
  mutate(deGroot_1 = ifelse(deGroot_1 == "Important (3)", "3", deGroot_1)) %>%
  mutate(deGroot_1 = ifelse(deGroot_1 == "Not important (0)", "0", deGroot_1)) %>%
  mutate(deGroot_1 = ifelse(deGroot_1 == "Of supreme importance (7)", "7", deGroot_1)) %>%
  mutate(deGroot_1 = ifelse(deGroot_1 == "Opposed to my Values (-1)", "-1", deGroot_1)) %>%
  mutate(deGroot_1 = ifelse(deGroot_1 == "Very important (6)", "6", deGroot_1)) %>%
  mutate(deGroot_1 = as.numeric(deGroot_1)) %>%
  mutate(deGroot_1 = deGroot_1 + 1)
  
mydata %>%
  filter(Gender != "#N/A") %>%
  ggplot(aes(x = deGroot_1)) +
  geom_density(aes(color = Gender), size = 2) +
  facet_wrap(~RaceEthnicity) +
  ylab("Density") +
  xlab("0 = Opposed to my Values, 8 = Of Supreme Importance") +
  ggtitle("Influential: Having an Impact On People's Lives") +
  theme_classic() 


```

```{r}

### Ambitious Corrected

mydata = mydata %>%
  filter(deGroot_13 != "-99") %>%
  mutate(deGroot_13 = ifelse(deGroot_13 == "Important (3)", "3", deGroot_13)) %>%
  mutate(deGroot_13 = ifelse(deGroot_13 == "Not important (0)", "0", deGroot_13)) %>%
  mutate(deGroot_13 = ifelse(deGroot_13 == "Of supreme importance (7)", "7", deGroot_13)) %>%
  mutate(deGroot_13 = ifelse(deGroot_13 == "Opposed to my Values (-1)", "-1", deGroot_13)) %>%
  mutate(deGroot_13 = ifelse(deGroot_13 == "Very important (6)", "6", deGroot_13)) %>%
  mutate(deGroot_13 = as.numeric(deGroot_13)) %>%
  mutate(deGroot_13 = deGroot_13 + 1)

mydata %>%
  filter(Gender != "#N/A") %>%
  ggplot(aes(x = deGroot_13)) +
  geom_density(aes(color = Gender), size = 2) +
  facet_wrap(~RaceEthnicity) +
  ylab("Density") +
  xlab("0 = Opposed to my Values, 8 = Of Supreme Importance") +
  ggtitle("Ambitious: Hardowrking, Aspiring") +
  theme_classic() 


```


# deGroot Altriustic Values

```{r}

### Equality Corrected

mydata = mydata %>%
  filter(deGroot_6 != "-99") %>%
  mutate(deGroot_6 = ifelse(deGroot_6 == "Important (3)", "3", deGroot_6)) %>%
  mutate(deGroot_6 = ifelse(deGroot_6 == "Not important (0)", "0", deGroot_6)) %>%
  mutate(deGroot_6 = ifelse(deGroot_6 == "Of supreme importance (7)", "7", deGroot_6)) %>%
  mutate(deGroot_6 = ifelse(deGroot_6 == "Opposed to my Values (-1)", "-1", deGroot_6)) %>%
  mutate(deGroot_6 = ifelse(deGroot_6 == "Very important (6)", "6", deGroot_6)) %>%
  mutate(deGroot_6 = as.numeric(deGroot_6)) %>%
  mutate(deGroot_6 = deGroot_6 + 1)

mydata %>%
  filter(Gender != "#N/A") %>%
  ggplot(aes(x = deGroot_6)) +
  geom_density(aes(color = Gender), size = 2) +
  facet_wrap(~RaceEthnicity) +
  ylab("Density") +
  xlab("0 = Opposed to my Values, 8 = Of Supreme Importance") +
  ggtitle("Equality: Equal Opportunity for All") +
  theme_classic() 


```

```{r}

### World Peace Corrected

mydata = mydata %>%
  filter(deGroot_7 != "-99") %>%
  mutate(deGroot_7 = ifelse(deGroot_7 == "Important (3)", "3", deGroot_7)) %>%
  mutate(deGroot_7 = ifelse(deGroot_7 == "Not important (0)", "0", deGroot_7)) %>%
  mutate(deGroot_7 = ifelse(deGroot_7 == "Of supreme importance (7)", "7", deGroot_7)) %>%
  mutate(deGroot_7 = ifelse(deGroot_7 == "Opposed to my Values (-1)", "-1", deGroot_7)) %>%
  mutate(deGroot_7 = ifelse(deGroot_7 == "Very important (6)", "6", deGroot_7)) %>%
  mutate(deGroot_7 = as.numeric(deGroot_7)) %>%
  mutate(deGroot_7 = deGroot_7 + 1)

mydata %>%
  filter(Gender != "#N/A") %>%
  ggplot(aes(x = deGroot_7)) +
  geom_density(aes(color = Gender), size = 2) +
  facet_wrap(~RaceEthnicity) +
  ylab("Density") +
  xlab("0 = Opposed to my Values, 8 = Of Supreme Importance") +
  ggtitle("World Peace: Free of War and Conflict") +
  theme_classic() 


```

```{r}

### Social Justice Corrected

mydata = mydata %>%
  filter(deGroot_9 != "-99") %>%
  mutate(deGroot_9 = ifelse(deGroot_9 == "Important (3)", "3", deGroot_9)) %>%
  mutate(deGroot_9 = ifelse(deGroot_9 == "Not important (0)", "0", deGroot_9)) %>%
  mutate(deGroot_9 = ifelse(deGroot_9 == "Of supreme importance (7)", "7", deGroot_9)) %>%
  mutate(deGroot_9 = ifelse(deGroot_9 == "Opposed to my Values (-1)", "-1", deGroot_9)) %>%
  mutate(deGroot_9 = ifelse(deGroot_9 == "Very important (6)", "6", deGroot_9)) %>%
  mutate(deGroot_9 = as.numeric(deGroot_9)) %>%
  mutate(deGroot_9 = deGroot_9 + 1)

mydata %>%
  filter(Gender != "#N/A") %>%
  ggplot(aes(x = deGroot_9)) +
  geom_density(aes(color = Gender), size = 2) +
  facet_wrap(~RaceEthnicity) +
  ylab("Density") +
  xlab("0 = Opposed to my Values, 8 = Of Supreme Importance") +
  ggtitle("Social Justice: Correcting Injustice, Care for the Weak") +
  theme_classic() 


```

```{r}

### Helpful Corrected

mydata = mydata %>%
  filter(deGroot_2 != "-99") %>%
  mutate(deGroot_2 = ifelse(deGroot_2 == "Important (3)", "3", deGroot_2)) %>%
  mutate(deGroot_2 = ifelse(deGroot_2 == "Not important (0)", "0", deGroot_2)) %>%
  mutate(deGroot_2 = ifelse(deGroot_2 == "Of supreme importance (7)", "7", deGroot_2)) %>%
  mutate(deGroot_2 = ifelse(deGroot_2 == "Opposed to my Values (-1)", "-1", deGroot_2)) %>%
  mutate(deGroot_2 = ifelse(deGroot_2 == "Very important (6)", "6", deGroot_2)) %>%
  mutate(deGroot_2 = as.numeric(deGroot_2)) %>%
  mutate(deGroot_2 = deGroot_2 + 1)

mydata %>%
  filter(Gender != "#N/A") %>%
  ggplot(aes(x = deGroot_2)) +
  geom_density(aes(color = Gender), size = 2) +
  facet_wrap(~RaceEthnicity) +
  ylab("Density") +
  xlab("0 = Opposed to my Values, 8 = Of Supreme Importance") +
  ggtitle("Helpful: Working for the Welfare of Others") +
  theme_classic() 


```

# deGroot Biospheric Values

```{r}

### Preventing Pollution Corrected

mydata = mydata %>%
  filter(deGroot_11 != "-99") %>%
  mutate(deGroot_11 = ifelse(deGroot_11 == "Important (3)", "3", deGroot_11)) %>%
  mutate(deGroot_11 = ifelse(deGroot_11 == "Not important (0)", "0", deGroot_11)) %>%
  mutate(deGroot_11 = ifelse(deGroot_11 == "Of supreme importance (7)", "7", deGroot_11)) %>%
  mutate(deGroot_11 = ifelse(deGroot_11 == "Opposed to my Values (-1)", "-1", deGroot_11)) %>%
  mutate(deGroot_11 = ifelse(deGroot_11 == "Very important (6)", "6", deGroot_11)) %>%
  mutate(deGroot_11 = as.numeric(deGroot_11)) %>%
  mutate(deGroot_11 = deGroot_11 + 1)

mydata %>%
  filter(Gender != "#N/A") %>%
  ggplot(aes(x = deGroot_11)) +
  geom_density(aes(color = Gender), size = 2) +
  facet_wrap(~RaceEthnicity) +
  ylab("Density") +
  xlab("0 = Opposed to my Values, 8 = Of Supreme Importance") +
  ggtitle("Preventing Pollution: Protecting Natural Resources") +
  theme_classic() 


```

```{r}

### Respecting the Earth Corrected

mydata = mydata %>%
  filter(deGroot_12 != "-99") %>%
  mutate(deGroot_12 = ifelse(deGroot_12 == "Important (3)", "3", deGroot_12)) %>%
  mutate(deGroot_12 = ifelse(deGroot_12 == "Not important (0)", "0", deGroot_12)) %>%
  mutate(deGroot_12 = ifelse(deGroot_12 == "Of supreme importance (7)", "7", deGroot_12)) %>%
  mutate(deGroot_12 = ifelse(deGroot_12 == "Opposed to my Values (-1)", "-1", deGroot_12)) %>%
  mutate(deGroot_12 = ifelse(deGroot_12 == "Very important (6)", "6", deGroot_12)) %>%
  mutate(deGroot_12 = as.numeric(deGroot_12)) %>%
  mutate(deGroot_12 = deGroot_12 + 1)

mydata %>%
  filter(Gender != "#N/A") %>%
  ggplot(aes(x = deGroot_12)) +
  geom_density(aes(color = Gender), size = 2) +
  facet_wrap(~RaceEthnicity) +
  ylab("Density") +
  xlab("0 = Opposed to my Values, 8 = Of Supreme Importance") +
  ggtitle("Respecting the Earth: Harmony with Other Species") +
  theme_classic() 


```

```{r}

### Unity with Nature Corrected

mydata = mydata %>%
  filter(deGroot_8 != "-99") %>%
  mutate(deGroot_8 = ifelse(deGroot_8 == "Important (3)", "3", deGroot_8)) %>%
  mutate(deGroot_8 = ifelse(deGroot_8 == "Not important (0)", "0", deGroot_8)) %>%
  mutate(deGroot_8 = ifelse(deGroot_8 == "Of supreme importance (7)", "7", deGroot_8)) %>%
  mutate(deGroot_8 = ifelse(deGroot_8 == "Opposed to my Values (-1)", "-1", deGroot_8)) %>%
  mutate(deGroot_8 = ifelse(deGroot_8 == "Very important (6)", "6", deGroot_8)) %>%
  mutate(deGroot_8 = as.numeric(deGroot_8)) %>%
  mutate(deGroot_8 = deGroot_8 + 1)

mydata %>%
  filter(Gender != "#N/A") %>%
  ggplot(aes(x = deGroot_8)) +
  geom_density(aes(color = Gender), size = 2) +
  facet_wrap(~RaceEthnicity) +
  ylab("Density") +
  xlab("0 = Opposed to my Values, 8 = Of Supreme Importance") +
  ggtitle("Unity with Nature: Fitting Into Nature") +
  theme_classic() 


```

```{r}

### Protecting the Environment Corrected

mydata = mydata %>%
  filter(deGroot_10 != "-99") %>%
  mutate(deGroot_10 = ifelse(deGroot_10 == "Important (3)", "3", deGroot_10)) %>%
  mutate(deGroot_10 = ifelse(deGroot_10 == "Not important (0)", "0", deGroot_10)) %>%
  mutate(deGroot_10 = ifelse(deGroot_10 == "Of supreme importance (7)", "7", deGroot_10)) %>%
  mutate(deGroot_10 = ifelse(deGroot_10 == "Opposed to my Values (-1)", "-1", deGroot_10)) %>%
  mutate(deGroot_10 = ifelse(deGroot_10 == "Very important (6)", "6", deGroot_10)) %>%
  mutate(deGroot_10 = as.numeric(deGroot_10)) %>%
  mutate(deGroot_10 = deGroot_10 + 1)

mydata %>%
  filter(Gender != "#N/A") %>%
  ggplot(aes(x = deGroot_10)) +
  geom_density(aes(color = Gender), size = 2) +
  facet_wrap(~RaceEthnicity) +
  ylab("Density") +
  xlab("0 = Opposed to my Values, 8 = Of Supreme Importance") +
  ggtitle("Protecting the Environment: Preserving Nature") +
  theme_classic() 


```


# Correlation Between deGroot Values and Sustainability Dimensions

```{r}

mydata = mydata %>%
  mutate(AveEgo = (deGroot_3 + deGroot_4 + deGroot_5 + deGroot_1 +deGroot_13)/5) %>%
  mutate(AveAlt = (deGroot_6 + deGroot_7 + deGroot_9 + deGroot_2)/4) %>%
  mutate(AveBio = (deGroot_11 + deGroot_12 + deGroot_8 + deGroot_10)/4)


egodata = mydata%>%
  select(AveEgo, AveAlt, AveBio, Q102_1, Q102_2, Q102_3) %>%
  rename("Egoistic Values" = AveEgo) %>%
  rename("Altruistic Values" = AveAlt) %>%
  rename("Biospheric Values" = AveBio) %>%
  rename(Environmental = Q102_1) %>%
  rename(Economic = Q102_2) %>%
  rename(Social = Q102_3)

corr1 = round(cor(egodata), 2)

ggcorrplot(corr1, type = "lower",
   lab = TRUE) 

```

# Correlation Between Values and Party Affiliation

```{r}

mydata = mydata %>%
  mutate(AveEgo = (deGroot_3 + deGroot_4 + deGroot_5 + deGroot_1 +deGroot_13)/5) %>%
  mutate(AveAlt = (deGroot_6 + deGroot_7 + deGroot_9 + deGroot_2)/4) %>%
  mutate(AveBio = (deGroot_11 + deGroot_12 + deGroot_8 + deGroot_10)/4)


egodata = mydata%>%
  select(AveEgo, AveAlt, AveBio, Pol.aff) %>%
  filter(Pol.aff != "-99") %>%
  filter(Pol.aff != "Other (please describe):") %>%
  filter(Pol.aff != "Libertarian") %>%
  filter(Pol.aff != "Independent (no leanings toward either party)") %>%
  mutate(Pol.aff = ifelse(Pol.aff == "Democrat", 0, 1)) %>%
  mutate(Pol.aff = as.numeric(Pol.aff)) %>%
  rename("Egoistic Values" = AveEgo) %>%
  rename("Altruistic Values" = AveAlt) %>%
  rename("Biospheric Values" = AveBio) %>%
  rename("Affiliates as Republican" = Pol.aff)

corr1 = round(cor(egodata), 2)

ggcorrplot(corr1, type = "lower",
   lab = TRUE) 

```

# Correlation Between deGroot and Interest in Food, Agriculture, Energy, and Water

```{r}

Q96data = mydata%>%
  select(AveEgo, AveAlt, AveBio, Q96_1, Q96_2, Q96_3, Q96_4) %>%
  rename("Egoistic Values" = AveEgo) %>%
  rename("Altruistic Values" = AveAlt) %>%
  rename("Biospheric Values" = AveBio) %>%
  filter(Q96_1 != "-99") %>%
  filter(Q96_2 != "-99") %>%
  filter(Q96_3 != "-99") %>%
  filter(Q96_4 != "-99") %>%
  mutate(Q96_1 = ifelse(Q96_1 == "A good deal", 4, Q96_1)) %>%
  mutate(Q96_1 = ifelse(Q96_1 == "A great deal", 5, Q96_1)) %>%
  mutate(Q96_1 = ifelse(Q96_1 == "A little", 2, Q96_1)) %>%
  mutate(Q96_1 = ifelse(Q96_1 == "A moderate amount", 3, Q96_1)) %>%
  mutate(Q96_1 = ifelse(Q96_1 == "Not at all", 1, Q96_1)) %>%
  mutate(Q96_1 = as.numeric(Q96_1)) %>%
  mutate(Q96_2 = ifelse(Q96_2 == "A good deal", 4, Q96_2)) %>%
  mutate(Q96_2 = ifelse(Q96_2 == "A great deal", 5, Q96_2)) %>%
  mutate(Q96_2 = ifelse(Q96_2 == "A little", 2, Q96_2)) %>%
  mutate(Q96_2 = ifelse(Q96_2 == "A moderate amount", 3, Q96_2)) %>%
  mutate(Q96_2 = ifelse(Q96_2 == "Not at all", 1, Q96_2)) %>%
  mutate(Q96_2 = as.numeric(Q96_2)) %>%
  mutate(Q96_3 = ifelse(Q96_3 == "A good deal", 4, Q96_3)) %>%
  mutate(Q96_3 = ifelse(Q96_3 == "A great deal", 5, Q96_3)) %>%
  mutate(Q96_3 = ifelse(Q96_3 == "A little", 2, Q96_3)) %>%
  mutate(Q96_3 = ifelse(Q96_3 == "A moderate amount", 3, Q96_3)) %>%
  mutate(Q96_3 = ifelse(Q96_3 == "Not at all", 1, Q96_3))%>%
  mutate(Q96_3 = as.numeric(Q96_3)) %>%
  mutate(Q96_4 = ifelse(Q96_4 == "A good deal", 4, Q96_4)) %>%
  mutate(Q96_4 = ifelse(Q96_4 == "A great deal", 5, Q96_4)) %>%
  mutate(Q96_4 = ifelse(Q96_4 == "A little", 2, Q96_4)) %>%
  mutate(Q96_4 = ifelse(Q96_4 == "A moderate amount", 3, Q96_4)) %>%
  mutate(Q96_4 = ifelse(Q96_4 == "Not at all", 1, Q96_4)) %>%
  mutate(Q96_4 = as.numeric(Q96_4)) %>%
  rename("Food" = Q96_1) %>%
  rename("Agriculture" = Q96_2) %>%
  rename("Energy" = Q96_3) %>%
  rename("Water" = Q96_4)
  

corr1 = round(cor(Q96data), 2)

ggcorrplot(corr1, type = "lower",
   lab = TRUE) +
  ggtitle("deGroot Values and Interest in Nexus")

Q96data %>%
  ggplot(aes(x = jitter(Q96data$`Egoistic Values`))) +
  geom_point(aes(y = jitter(Food)), color = 'red', alpha = .2) +
  geom_point(aes(y = jitter(Agriculture)), color = 'yellow', alpha = .2) +
  geom_point(aes(y = jitter(Energy)), color = 'green', alpha = .2) +
  geom_point(aes(y = jitter(Water)), color = 'blue', alpha = .2) +
  geom_smooth(aes(x = Q96data$`Egoistic Values`, y = Food), method = "lm", se = F, color = 'red') +
  geom_smooth(aes(x = Q96data$`Egoistic Values`, y = Agriculture), method = "lm", se = F, color = 'yellow') +
  geom_smooth(aes(x = Q96data$`Egoistic Values`, y = Energy), method = "lm", se = F, color = 'green') + geom_smooth(aes(x = Q96data$`Egoistic Values`, y = Water), method = "lm", se = F, color = 'blue') +
  xlab("Egoistic Values") +
  ylab("Food = red, Agriculture = yellow, Energy = green, Water = Blue") +
  ggtitle("Egoistic Values Versus Interest in Nexus") +
  theme_classic()

Q96data %>%
  ggplot(aes(x = jitter(Q96data$`Altruistic Values`))) +
  geom_point(aes(y = jitter(Food)), color = 'red', alpha = .2) +
  geom_point(aes(y = jitter(Agriculture)), color = 'yellow', alpha = .2) +
  geom_point(aes(y = jitter(Energy)), color = 'green', alpha = .2) +
  geom_point(aes(y = jitter(Water)), color = 'blue', alpha = .2) +
  geom_smooth(aes(x = Q96data$`Altruistic Values`, y = Food), method = "lm", se = F, color = 'red') +
  geom_smooth(aes(x = Q96data$`Altruistic Values`, y = Agriculture), method = "lm", se = F, color = 'yellow') +
  geom_smooth(aes(x = Q96data$`Altruistic Values`, y = Energy), method = "lm", se = F, color = 'green') + geom_smooth(aes(x = Q96data$`Altruistic Values`, y = Water), method = "lm", se = F, color = 'blue') +
  xlab("Altruistic Values") +
  ylab("Food = red, Agriculture = yellow, Energy = green, Water = Blue") +
  ggtitle("Altruistic Values Versus Interest in Nexus") +
  theme_classic()

Q96data %>%
  ggplot(aes(x = jitter(Q96data$`Biospheric Values`))) +
  geom_point(aes(y = jitter(Food)), color = 'red', alpha = .2) +
  geom_point(aes(y = jitter(Agriculture)), color = 'yellow', alpha = .2) +
  geom_point(aes(y = jitter(Energy)), color = 'green', alpha = .2) +
  geom_point(aes(y = jitter(Water)), color = 'blue', alpha = .2) +
  geom_smooth(aes(x = Q96data$`Biospheric Values`, y = Food), method = "lm", se = F, color = 'red') +
  geom_smooth(aes(x = Q96data$`Biospheric Values`, y = Agriculture), method = "lm", se = F, color = 'yellow') +
  geom_smooth(aes(x = Q96data$`Biospheric Values`, y = Energy), method = "lm", se = F, color = 'green') + geom_smooth(aes(x = Q96data$`Biospheric Values`, y = Water), method = "lm", se = F, color = 'blue') +
  xlab("Biospheric Values") +
  ylab("Food = red, Agriculture = yellow, Energy = green, Water = Blue") +
  ggtitle("Biospheric Values Versus Interest in Nexus") +
  theme_classic()

```



# Behaviors

```{r}

#### Walk instead of Drive

mydata %>%
  filter(Behavior_1 != "-99") %>%
  filter(Gender != "#N/A") %>%
  filter(Gender != "#Name?") %>%
  ggplot(aes(x = Behavior_1, fill = Gender)) +
  geom_bar() +
  facet_wrap(~RaceEthnicity) +
  xlab("How often do you do these behaviors?") +
  ylab("Count") +
  ggtitle("Walk, Bike, or Take Public Transportation Instead of Driving, By Race and Gender") +
  theme_classic() +
  scale_x_discrete(limits=c("Never", "Rarely", "Sometimes",
                            "Often", "Always")) +
   theme(axis.text.x = element_text(angle=90))


```

```{r}

#### Eat Organic Food

mydata %>%
  filter(Behavior_2 != "-99") %>%
  filter(Gender != "#N/A") %>%
  filter(Gender != "#Name?") %>%
  ggplot(aes(x = Behavior_2, fill = Gender)) +
  geom_bar() +
  facet_wrap(~RaceEthnicity) +
  xlab("How often do you do these behaviors?") +
  ylab("Count") +
  ggtitle("Eat Organic Food, by Race and Gender") +
  theme_classic() +
  scale_x_discrete(limits=c("Never", "Rarely", "Sometimes",
                            "Often", "Always")) +
   theme(axis.text.x = element_text(angle=90))

```

```{r}

#### Eat Meat

mydata %>%
  filter(Behavior_3 != "-99") %>%
  filter(Gender != "#N/A") %>%
  filter(Gender != "#Name?") %>%
  ggplot(aes(x = Behavior_3, fill = Gender)) +
  geom_bar() +
  facet_wrap(~RaceEthnicity) +
  xlab("How often do you do these behaviors?") +
  ylab("Count") +
  ggtitle("Eat Meat, by Race and Gender") +
  theme_classic() +
  scale_x_discrete(limits=c("Never", "Rarely", "Sometimes",
                            "Often", "Always")) +
   theme(axis.text.x = element_text(angle=90))


```

```{r}

#### Eat Milk Cheese Yogurt

mydata %>%
  filter(Behavior_4 != "-99") %>%
  filter(Gender != "#N/A") %>%
  filter(Gender != "#Name?") %>%
  ggplot(aes(x = Behavior_4, fill = Gender)) +
  geom_bar() +
  facet_wrap(~RaceEthnicity) +
  xlab("How often do you do these behaviors?") +
  ylab("Count") +
  ggtitle("Eat Milk, Cheese, Eggs, or Yogurt, By Race and Gender") +
  theme_classic() +
  scale_x_discrete(limits=c("Never", "Rarely", "Sometimes",
                            "Often", "Always")) +
   theme(axis.text.x = element_text(angle=90))

```

```{r}

#### Print on Both Sides of Paper

mydata %>%
  filter(Behavior_5 != "-99") %>%
  filter(Gender != "#N/A") %>%
  filter(Gender != "#Name?") %>%
  ggplot(aes(x = Behavior_5, fill = Gender)) +
  geom_bar() +
  facet_wrap(~RaceEthnicity) +
  xlab("How often do you do these behaviors?") +
  ylab("Count") +
  ggtitle("Print on Both Sides of the Paper, By Race and Gender") +
  theme_classic() +
  scale_x_discrete(limits=c("Never", "Rarely", "Sometimes",
                            "Often", "Always")) +
   theme(axis.text.x = element_text(angle=90))

```

```{r}

#### Carry a Reusable Water Bottle

mydata %>%
  filter(Behavior_6 != "-99") %>%
  filter(Gender != "#N/A") %>%
  filter(Gender != "#Name?") %>%
  ggplot(aes(x = Behavior_6, fill = Gender)) +
  geom_bar() +
  facet_wrap(~RaceEthnicity) +
  xlab("How often do you do these behaviors?") +
  ylab("Count") +
  ggtitle("Carry a Reusable Watter Bottle, By Race and Gender") +
  theme_classic() +
  scale_x_discrete(limits=c("Never", "Rarely", "Sometimes",
                            "Often", "Always")) +
   theme(axis.text.x = element_text(angle=90))

```

```{r}

#### Purchase Used Instead of New

mydata %>%
  filter(Behavior_7 != "-99") %>%
  filter(Gender != "#N/A") %>%
  filter(Gender != "#Name?") %>%
  ggplot(aes(x = Behavior_7, fill = Gender)) +
  geom_bar() +
  facet_wrap(~RaceEthnicity) +
  xlab("How often do you do these behaviors?") +
  ylab("Count") +
  ggtitle("Purchase Used Instead of New, By Race and Gender") +
  theme_classic() +
  scale_x_discrete(limits=c("Never", "Rarely", "Sometimes",
                            "Often", "Always")) +
   theme(axis.text.x = element_text(angle=90))

```

```{r}

#### Use Reusable bags when shopping

mydata %>%
  filter(Behavior_8 != "-99") %>%
  filter(Gender != "#N/A") %>%
  filter(Gender != "#Name?") %>%
  ggplot(aes(x = Behavior_8, fill = Gender)) +
  geom_bar() +
  facet_wrap(~RaceEthnicity) +
  xlab("How often do you do these behaviors?") +
  ylab("Count") +
  ggtitle("Use Reusable BagesWhen Shopping, By Race and Gender") +
  theme_classic() +
  scale_x_discrete(limits=c("Never", "Rarely", "Sometimes",
                            "Often", "Always")) +
   theme(axis.text.x = element_text(angle=90))

```

```{r}

#### Sort Recycling

mydata %>%
  filter(Behavior_9 != "-99") %>%
  filter(Gender != "#N/A") %>%
  filter(Gender != "#Name?") %>%
  ggplot(aes(x = Behavior_9, fill = Gender)) +
  geom_bar() +
  facet_wrap(~RaceEthnicity) +
  xlab("How often do you do these behaviors?") +
  ylab("Count") +
  ggtitle("Sort Recycling, By Race and Gender") +
  theme_classic() +
  scale_x_discrete(limits=c("Never", "Rarely", "Sometimes",
                            "Often", "Always")) +
   theme(axis.text.x = element_text(angle=90))

```

```{r}

#### Turn of Lights in an Empty Room 

mydata %>%
  filter(Behavior_10 != "-99") %>%
  filter(Gender != "#N/A") %>%
  filter(Gender != "#Name?") %>%
  ggplot(aes(x = Behavior_10, fill = Gender)) +
  geom_bar() +
  facet_wrap(~RaceEthnicity) +
  xlab("How often do you do these behaviors?") +
  ylab("Count") +
  ggtitle("Turn Off Lights in an Empty Room Where You Live, By Race and Gender") +
  theme_classic() +
  scale_x_discrete(limits=c("Never", "Rarely", "Sometimes",
                            "Often", "Always")) +
   theme(axis.text.x = element_text(angle=90))

```

```{r}

#### Turn your electronics off or low power mode

mydata %>%
  filter(Behavior_11 != "-99") %>%
  filter(Gender != "#N/A") %>%
  filter(Gender != "#Name?") %>%
  ggplot(aes(x = Behavior_11, fill = Gender)) +
  geom_bar() +
  facet_wrap(~RaceEthnicity) +
  xlab("How often do you do these behaviors?") +
  ylab("Count") +
  ggtitle("Turn Electronics Off when not in Use, By Race and Gender") +
  theme_classic() +
  scale_x_discrete(limits=c("Never", "Rarely", "Sometimes",
                            "Often", "Always")) +
   theme(axis.text.x = element_text(angle=90))

```

```{r}

#### Use Stairs when Going More Than One Floor

mydata %>%
  filter(Behavior_12 != "-99") %>%
  filter(Gender != "#N/A") %>%
  filter(Gender != "#Name?") %>%
  ggplot(aes(x = Behavior_12, fill = Gender)) +
  geom_bar() +
  facet_wrap(~RaceEthnicity) +
  xlab("How often do you do these behaviors?") +
  ylab("Count") +
  ggtitle("Use the Stairs When Going More Than One Floor, By Race and Gender") +
  theme_classic() +
  scale_x_discrete(limits=c("Never", "Rarely", "Sometimes",
                            "Often", "Always")) +
   theme(axis.text.x = element_text(angle=90))

```

```{r}

#### Act to conserve water

mydata %>%
  filter(Behavior_13 != "-99") %>%
  filter(Gender != "#N/A") %>%
  filter(Gender != "#Name?") %>%
  ggplot(aes(x = Behavior_13, fill = Gender)) +
  geom_bar() +
  facet_wrap(~RaceEthnicity) +
  xlab("How often do you do these behaviors?") +
  ylab("Count") +
  ggtitle("Act to Conserve Water When Doing Chores, By Race and Gender") +
  theme_classic() +
  scale_x_discrete(limits=c("Never", "Rarely", "Sometimes",
                            "Often", "Always")) +
   theme(axis.text.x = element_text(angle=90))

```

```{r}

#### Limit your consumption of new items

mydata %>%
  filter(Behavior_14 != "-99") %>%
  filter(Gender != "#N/A") %>%
  filter(Gender != "#Name?") %>%
  ggplot(aes(x = Behavior_14, fill = Gender)) +
  geom_bar() +
  facet_wrap(~RaceEthnicity) +
  xlab("How often do you do these behaviors?") +
  ylab("Count") +
  ggtitle("Limit Your Consumption of New Items, By Race and Gender") +
  theme_classic() +
  scale_x_discrete(limits=c("Never", "Rarely", "Sometimes",
                            "Often", "Always")) +
   theme(axis.text.x = element_text(angle=90))

```

```{r}

#### Limit the Energy Used for Heat or AC

mydata %>%
  filter(Behavior_15 != "-99") %>%
  filter(Gender != "#N/A") %>%
  filter(Gender != "#Name?") %>%
  ggplot(aes(x = Behavior_15, fill = Gender)) +
  geom_bar() +
  facet_wrap(~RaceEthnicity) +
  xlab("How often do you do these behaviors?") +
  ylab("Count") +
  ggtitle("Limit the Energy Used for Haat or AC, By Race and Gender") +
  theme_classic() +
  scale_x_discrete(limits=c("Never", "Rarely", "Sometimes",
                            "Often", "Always")) +
   theme(axis.text.x = element_text(angle=90))

```

# Diet

```{r}

#### Limit the Energy Used for Heat or AC

mydata$Diet = as.factor(mydata$Diet)
levels(mydata$Diet) = c("Lifestyle Vegan" ,"Omnivorous",
                        "Semi-Vegetarian", "Strict Vegetarian", "Vegetarian", "-99")

mydata %>%
  filter(Diet != "-99") %>%
  filter(Gender != "#N/A") %>%
  filter(Gender != "#Name?") %>%
  ggplot(aes(x = Diet, fill = Gender)) +
  geom_bar() +
  facet_wrap(~RaceEthnicity) +
  theme_classic() +
  ylab("Count") +
  ggtitle("Diet, By Race and Gender")+
   theme(axis.text.x = element_text(angle=90)) +
  scale_x_discrete(limits=c("Lifestyle Vegan", "Strict Vegetarian", "Vegetarian",
                            "Semi-Vegetarian", "Omnivorous"))
```



